Torontonians Prefer to Get Married in the Warmer Half of the Year

### 2024-01-25 outputs/paper/paper.qmd
updates

raw_marriage_data <- read_csv("/cloud/project/inputs/data/unedited_data.csv")
gt(head(raw_marriage_data))

@@

cleaned_marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
gt(head(cleaned_marriage_data_2022))
```
After the data I need has been cleaned, it is saved into 3 .csv files, one for 2022, another for 2023, and the third contains both years. The only columns that remain in any file are Date and Marriages (@fig-cleaned_toronto_marriages_2022).

@@

## 2022
```{r}
#| label: fig-2022_marriages
#| fig-cap: Trend in marriage licenses issued over time in 2022
#| echo: false
#| message: false
#| eval: true
#| warning: false
marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")

@@

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  scale_x_discrete(breaks=c("2022-April-01", "2022-September-01")) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5), plot.title = element_text(size=12)) +
  labs(x = "Month", y = "Marriages", color = "Country", title = "Marriage Licenses Issued in Toronto in 2022")
```
```{r}
#| echo: false
#| message: false
#| include: false
marriage_data_2022 <- read_csv("/cloud/project/outputs/data/cleaned_data_2022.csv")
summary(marriage_data_2022$Marriages)
sum(marriage_data_2022$Marriages)
```

@@

## 2023
```{r}
#| label: fig-2023_marriages
#| fig-cap: Trend in marriage licenses issued over time in 2023
#| echo: false
#| message: false
#| eval: true
#| warning: false
marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")

@@

```{r}
#| echo: false
#| message: false
#| include: false
marriage_data_2023 <- read_csv("/cloud/project/outputs/data/cleaned_data_2023.csv")
summary(marriage_data_2023$Marriages)
sum(marriage_data_2023$Marriages)
```

@@

## Both Years
```{r}
#| label: fig-marriages
#| fig-cap: Trend in marriage licenses issued over time from 2022 to 2023
#| echo: false
#| message: false
#| eval: true
#| warning: false
marriage_data <- read_csv("/cloud/project/outputs/data/cleaned_data_all_years.csv")

>>>>

raw_marriage_data <- read_csv("/inputs/data/unedited_data.csv")
gt(head(raw_marriage_data))

@@

cleaned_marriage_data_2022 <- read_csv("/outputs/data/cleaned_data_2022.csv")
gt(head(cleaned_marriage_data_2022))
```
After the data I need has been cleaned, it is saved into 3 .csv files, one for 2022, another for 2023, and the third contains both years. The only columns that remain in any file are Date and Marriages (@fig-cleaned_toronto_marriages_2022).

@@

## 2022
```{r}
#| label: fig-2022_marriages
#| fig-cap: Trend in marriage licenses issued over time in 2022
#| echo: false
#| message: false
#| eval: true
#| warning: false
marriage_data <- read_csv("/outputs/data/cleaned_data_2022.csv")

@@

marriage_data |>
  ggplot(aes(x = Date, y = Marriages, label = Marriages)) +
  geom_point() +
  geom_text(hjust=0, vjust=0) +
  scale_x_discrete(breaks=c("2022-April-01", "2022-September-01")) +
  theme(axis.text.x = element_text(angle = 0, vjust = 0.5), plot.title = element_text(size=12)) +
  labs(x = "Month", y = "Marriages", color = "Country", title = "Marriage Licenses Issued in Toronto in 2022")
```
```{r}
#| echo: false
#| message: false
#| include: false
marriage_data_2022 <- read_csv("/outputs/data/cleaned_data_2022.csv")
summary(marriage_data_2022$Marriages)
sum(marriage_data_2022$Marriages)
```

@@

## 2023
```{r}
#| label: fig-2023_marriages
#| fig-cap: Trend in marriage licenses issued over time in 2023
#| echo: false
#| message: false
#| eval: true
#| warning: false
marriage_data <- read_csv("/outputs/data/cleaned_data_2023.csv")

@@

```{r}
#| echo: false
#| message: false
#| include: false
marriage_data_2023 <- read_csv("/outputs/data/cleaned_data_2023.csv")
summary(marriage_data_2023$Marriages)
sum(marriage_data_2023$Marriages)
```

@@

## Both Years
```{r}
#| label: fig-marriages
#| fig-cap: Trend in marriage licenses issued over time from 2022 to 2023
#| echo: false
#| message: false
#| eval: true
#| warning: false
marriage_data <- read_csv("/outputs/data/cleaned_data_all_years.csv")
